A Classical Density-Functional Theory for Describing Water Interfaces

### 2013-08-02 papers/water-saft/paper.tex
Merged files.  Some changes to plots and plot descriptions in water. Tested everything on node36.

\begin{figure}
\begin{center}
\includegraphics[width=3.5in]{figs/density-compare}
\end{center}
\caption{ Density profiles for single rods of different
  radii for the new functional (top) and the old functional
  (bottom). Each separately colored line represents a density profile
  for a rod; the black dotted line is the bulk density.}
\label{fig:density-single-rod}
\end{figure}

@@

\begin{figure}
\begin{center}
\includegraphics[width=3.5in]{figs/single-rod-broken-HB}
\end{center}
\caption{ Broken hydrogen bonds broken when rods are placed in
  homogeneous water.  \fixme{Our old and new functional are both plotted here}}
\label{fig:single-rod-broken-HB}
\end{figure}

@@

\begin{figure}
\begin{center}
\includegraphics[width=3.5in]{figs/sphere-broken-HB}
\end{center}
\caption{ \fixme{spheres!}}
\label{fig:spheres-broken-HB}
\end{figure}

>>>>

\begin{figure}
\begin{center}
\includegraphics[width=3.5in]{figs/density-compare}
\end{center}
\caption{ Density profiles for a water around a single hydrophobic
  rod. The solid red profile is the density using our new functional
  and the dashed blue profile the result of our old functional.  For
  comparison, under the profiles is a cartoon of a string of hard
  spheres touching in one dimension. The horizontal black dotted line
  is the bulk density.}
\label{fig:density-single-rod}
\end{figure}

@@

\begin{figure}
\begin{center}
\includegraphics[width=3.5in]{figs/single-rod-broken-HB}
\end{center}
\caption{Broken hydrogen bonds per nanometer for various hydrophobic rods
  immeresed in water.  The solid red line uses our new functional
  while the dashed blue line uses the old one. For large enough rods,
  the graph increases linearly for both functionals.}
\label{fig:single-rod-broken-HB}
\end{figure}

@@

\begin{figure}
\begin{center}
\includegraphics[width=3.5in]{figs/sphere-broken-HB}
\end{center}
\caption{Broken hydrogen bonds per for various hard spheres
  immeresed in water.  The solid red line uses our new functional
  while the dashed blue line uses the old one.}
\label{fig:spheres-broken-HB}
\end{figure}
